An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-09-21 CMPSpaper_writing/CMPSpaper_writing.Rmd
get rid of warning

p.npeak_plot <- table.cmps_neapk.long %>%
  ggplot(aes(x = xstart + 3*as.numeric(factor(Metric))-9)) +
  geom_segment(aes(xend = xstart + 3*as.numeric(factor(Metric))-9, 
                   y = value, yend= 0, color=Metric),
               position=position_dodge(width = 0.6)) +
  geom_point(aes(y =  value, color = Metric, shape = rf_status), 
             alpha = 0.8,
             position=position_dodge(width = 0.5), size = 3.5) +
  facet_grid(.~study) +
  ylab("Sums of Squares Ratio") + 
  xlab("Number of Peaks") +
  coord_flip() +
  scale_x_continuous(breaks = npeak_convert$xstart, labels = npeak_convert$npeak ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  guides(shape = FALSE) + 
  scale_shape_manual(values = c(16, 1)) +
  scale_colour_manual(values=cols_2, labels = labels) +
  scale_fill_manual(values=cols_1, labels = labels) 
```

@@

```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3}
p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
  xlab(labels[3])
p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
  xlab(labels[4])
p.result1_44 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
               common.legend = TRUE, legend = "bottom")
p.result1_44 <- annotate_figure(p.result1_44, top = text_grob(com.title44))
p.result1_44
```

>>>>

p.npeak_plot <- table.cmps_neapk.long %>%
  ggplot(aes(x = xstart + 3*as.numeric(factor(Metric))-9)) +
  geom_segment(aes(xend = xstart + 3*as.numeric(factor(Metric))-9, 
                   y = value, yend= 0, color=Metric),
               position=position_dodge(width = 0.6)) +
  geom_point(aes(y =  value, color = Metric, shape = rf_status), 
             alpha = 0.8,
             position=position_dodge(width = 0.5), size = 3.5) +
  facet_grid(.~study) +
  ylab("Sums of Squares Ratio") + 
  xlab("Number of Peaks") +
  coord_flip() +
  scale_x_continuous(breaks = npeak_convert$xstart, labels = npeak_convert$npeak ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  guides(shape = "none") + 
  scale_shape_manual(values = c(16, 1)) +
  scale_colour_manual(values=cols_2, labels = labels) +
  scale_fill_manual(values=cols_1, labels = labels) 
```

@@

```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3, warning=FALSE}
p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
  xlab(labels[3])
p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
  xlab(labels[4])
p.result1_44 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
               common.legend = TRUE, legend = "bottom")
p.result1_44 <- annotate_figure(p.result1_44, top = text_grob(com.title44))
p.result1_44
```
